---
title: "Structured Expert Elicitation - SHELF Report"
format:
  html:
    toc: true
    code-fold: true
  pdf: default
params:
  study_id: ""
  question_id: ""
  round_number: 1
  anonymize: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
required <- c("mongolite", "jsonlite", "ggplot2", "SHELF", "knitr")
missing <- required[!vapply(required, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing)) {
  stop("Install required packages first: ", paste(missing, collapse = ", "))
}

root <- normalizePath("..", mustWork = TRUE)
setwd(root)
readRenviron(".Renviron")

r_files <- c(
  "config.R", "log.R", "ids.R", "mongo.R", "auth.R", "access.R",
  "tokens.R", "onboarding.R", "comments.R", "chips.R", "shelf.R",
  "studies.R", "reports.R", "survey_ui.R"
)
for (file in r_files) source(file.path("R", file), local = FALSE)

study <- find_study(params$study_id)
if (is.null(study)) stop("Study not found: ", params$study_id)
questions <- study_questions(doc_id(study))
question <- if (nzchar(params$question_id)) {
  matches <- Filter(function(q) identical(doc_id(q), params$question_id), questions)
  if (length(matches)) matches[[1]] else NULL
} else {
  primary_question(questions)
}
if (is.null(question)) stop("Question not found for this study.")

aggregation <- latest_aggregation(
  doc_id(study), doc_id(question), as.integer(params$round_number)
)
result <- aggregation_as_shelf_result(aggregation)
if (is.null(result)) stop("No SHELF aggregation is available for this study and round.")
params_table <- audit_params_df(result)
```

## Study

**Study:** `r study$title %||% ""`
**Question:** `r question$title %||% question$code`
**Round:** `r as.integer(params$round_number)`
**Generated:** `r iso_now()`

## Group summary

`r result$conclusion %||% "No conclusion was stored."`

## Parameter table

```{r}
display <- params_table
names(display) <- c(
  "Expert / result", "Role", "Lower quantile", "Median quantile",
  "Upper quantile", "Distribution", "Best fit from SHELF"
)
numeric_cols <- c("Lower quantile", "Median quantile", "Upper quantile")
display[numeric_cols] <- lapply(display[numeric_cols], function(x) {
  formatC(as.numeric(x), format = "fg", digits = 6, flag = "#")
})
knitr::kable(display, caption = "SHELF fitted quantiles")
```

## Density chart

```{r}
fit <- result$fit
plot_data <- shelf_plot_df(fit, "both")
if (is.null(plot_data)) {
  cat("No density data is available.")
} else {
  ggplot2::ggplot(
    plot_data,
    ggplot2::aes(x = x, y = pdf, colour = name, linetype = role, group = name)
  ) +
    ggplot2::geom_line(linewidth = 0.8) +
    ggplot2::theme_minimal(base_size = 12) +
    ggplot2::labs(
      x = "Value", y = "Density",
      colour = "Expert / result", linetype = "Role"
    )
}
```

## Notes

This report uses the stored aggregation from the Shiny platform. Expert labels
remain blinded when the stored SHELF result was anonymized.
